Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
edits to section 4

\usepackage{siunitx}
\usepackage[color]{changebar}
\usepackage{enumitem}
\usepackage[lighttt]{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

@@

\section{Probabilistic Program}
\label{sec:pp-def}

@@

A (almost-surely terminating) probabilistic program defines a probability distribution 
over finite feasible traces $\pmb{x}$. The distribution has the probability density 
$\pi(\pmb{x}) := \gamma(\pmb{x}) / Z$ where 
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j})
  \quad \mbox{for the image $\pmb{y}$ of $\pmb{x}$}, 
  \label{eqn:p-trace}
\end{align}
and $Z$ is the normalization constant $Z := \int \gamma(\pmb{x})d(\pmb{x})$
of $\gamma$.\footnote{The integral and the density use the default measure obtained by the standard extension of
a $\sigma$-finite measure on finite traces where the $\sigma$-finite measure itself is defined by
a countable sum of Lebesque and counting measures.}

>>>>

\usepackage{siunitx}
\usepackage[color]{changebar}
\usepackage{enumitem}
\usepackage[lighttt]{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
%\usepackage{microtype}

@@

\section{Probability of a Program Execution}
\label{sec:pp-def}

@@

A (almost-surely terminating) probabilistic program defines a probability distribution 
over finite feasible traces $\pmb{x}$ with probability density 
$\pi(\pmb{x}) := \gamma(\pmb{x}) / Z$ where 
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j})
  \quad \mbox{for the image $\pmb{y}$ of $\pmb{x}$}, 
  \label{eqn:p-trace}
\end{align}
and $Z$ is the normalization constant $Z := \int \gamma(\pmb{x})d(\pmb{x})$. The integral and the density use the default measure obtained by the standard extension of
a $\sigma$-finite measure on finite traces where the $\sigma$-finite measure itself is defined by
a countable sum of Lebesque and counting measures.
